\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\SubItem}[1]{
    {\setlength\itemindent{15pt} \item[-] #1}
}
\name{Canberk Arköse} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+36205007793 \\ Budapest} 
\address{\href{mailto:canberk.arkose@outlook.com}{canberk.arkose@outlook.com} \\ \href{https://www.linkedin.com/in/canberk-arkose}{linked.in/canberk} \\
\href{https://github.com/canberkarkose}{github/canberk}}


\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}

{ Focused Computer Science major with a 4.4/5 GPA, currently attending Eötvös Lorand University on a Stipendium Hungaricum Scholarship. 

I'm passionate about web development, I enjoy the creativity and problem-solving aspects of building beautiful and functional websites. I have experience with a range of web development technologies, including React, Javascript, PHP, and many others. 

In my previous projects, I have demonstrated a strong ability to design and develop user-friendly, responsive websites that meet the needs of clients and end-users.}


\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{{\bf Eötvös Loránd University, Budapest} \\
BSc Computer Science \\
Relevant Coursework:
\begin{itemize}
     \item Web Development(HTML,CSS), Web Programming(Javascript,PHP), Imperative Programming(C), \\Programming(C++), Programming Languages(Java), Operating Systems(C), Algorithms and Data Structures,
     \\Distributed Communication(Go), Application of Discrete Models(SageMath,Python)
     
 \end{itemize}}


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technologies & React, Javascript/jQuery, Java, Python, HTML/CSS, C/C++...
\\
Technical Skills & Web Programming, Programming Languages, Imperative Programming...
\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{IT Support} \hfill Jun 2019 - Sep 2019\\
Ak Metal Mimarlik \hfill \textit{Turkey}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Provided technical support to employees for all IT-related issues, including troubleshooting and resolving technical problems in a timely and efficient manner.

 \end{itemize}
 

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{PROJECTS}

\underline{React-App}
 \begin{itemize}
    \itemsep -3pt {} 
     \item A \textbf{web scraper} on mobile phone prices and brands from an online shop and displays the information in a \textbf{React-based} web app. 
     \item Technologies used include \textbf{Python} with BeautifulSoup and Requests for web scraping, a JSON file for data storage, and React with \textbf{react-table} for web app development.
 \end{itemize}

\underline{Voting Simulation}
 \begin{itemize}
    \itemsep -3pt {} 
     \item \textbf{A web application} that simulates voting, allowing users to cast their votes. Features include admin functionalities such as creating new polls. 
     \item Utilized \textbf{PHP} for back-end, \textbf{JavaScript}, HTML and CSS for front-end, and a JSON file for data storage.
 \end{itemize}
\underline{Light Bulb Placement Game}
 \begin{itemize}
    \itemsep -3pt {} 
     \item \textbf{A JavaScript game} where the goal is to place light bulbs to enlighten white blocks while following the rules on black blocks.
     \item Consists of 3 different levels, technologies used include Javascript, HTML, and CSS.
 \end{itemize}


 
\end{rSection} 

\end{document}
